Pillar 2- Quick Topic Models

### 2019-04-17 Pillar 2 - Tmp Topic Modeling.Rmd
spaces for readability of code

#Extract Distributions (Gamma/Beta)-----------------------------------------------
get_distributions <- function(model, distrib_str){ #input gamma or beta
  tidy(model, matrix = distrib_str)        %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(!!sym(distrib_str)))
}

#perplexity Function-----------------------------------------------
my_perplexity <- function(model, dtm){
  perplexity(model, dtm, estimate_theta = FALSE)
}

@@

get_top_terms_topic <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    select(topic, term) %>%
    group_by(topic) %>%
    summarise(top_words = list(term))

@@

get_top_topics_course <- function(d_gamma){
  data.frame(d_gamma) %>%
    group_by(document) %>%
    top_n(5, gamma) %>%
    select(document, topic) %>%
    summarise(top_topic = list(topic))
}

get_kw <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(3, beta) %>%
    ungroup()%>%
    pull(term)%>%
    unique()
}

@@

         #Document Term Matrix
         DTM        = pmap(.l = list(Origin), .f = extract_dtm)) %>%
  filter(Origin == which_texts) %>%
  mutate(
         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control), #my_control

@@

##Plots - Model Evaluation
To evaluate how many topics are optimal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = FALSE}
#Function
plot_evaluation <- function(origin){

@@

#App
For our Recommender System, we need to pass the distributions, number of topics, origin, and key words to the app.
##Distributions and Key words
The function `clean_kw` removes stopwords from our key words.
```{r function clean key words, eval = T}
clean_kw <- function(kw_list){

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort

@@

#rm(course_all, course_following_semester)
```
## Saving files for APP
We save all requirements for the app.
```{r app files, eval = T}
save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
```

>>>>

#Extract Distributions (Gamma/Beta)-----------------------------------------------
get_distributions <- function(model, distrib_str) { #input gamma or beta
  tidy(model, matrix = distrib_str) %>%
    mutate(topic = paste("Topic", topic) ) %>%
    arrange(topic, desc(!!sym(distrib_str)))
}

#perplexity Function-----------------------------------------------
my_perplexity <- function(model, dtm) {
  perplexity(model, dtm, estimate_theta = FALSE)
}

@@

get_top_terms_topic <- function(d_beta) {
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    select(topic, term) %>%
    group_by(topic) %>%
    summarise(top_words = list(term))

@@

get_top_topics_course <- function(d_gamma) {
  data.frame(d_gamma) %>%
    group_by(document) %>%
    top_n(5, gamma) %>%
    select(document, topic) %>%
    summarise(top_topic = list(topic))
}

get_kw <- function(d_beta) {
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(3, beta) %>%
    ungroup() %>%
    pull(term) %>%
    unique()
}

@@

tb_topic_model <- tibble( 
  n_topic = rep(topic_numbers, each = length(d_text)) 
  ) %>%

  mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

         #Document Term Matrix
         DTM        = pmap(.l = list(Origin), .f = extract_dtm)) %>%

  filter(Origin == which_texts) %>%

  mutate(
         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control), #my_control

@@

##Plots - Model Evaluation
To evaluate how many topics are optimal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = FALSE}
#Function
plot_evaluation <- function(origin) {

@@

#App
For our Recommender System, we need to pass the distributions, number of topics, origin, and key words to the app.
##Distributions and Key words
The function `clean_kw` removes stopwords from our key words.
```{r function clean key words, eval = T}
clean_kw <- function(kw_list) {

@@

#
##courses following_semester
course_following_semester <- sample(x = course_all,
                                    size    = 60,
                                    replace = FALSE) %>% 
  sort()

@@

app_model <- app_topic_model %>%
  filter(n_topic == 55)

#rm(course_all, course_following_semester)
```
## Saving files for APP
We save all requirements for the app.
```{r app files, eval = T}
save(app_topic_model, app_model, file = "App/Recommender System/data_topic_models.RDATA")
```
